---
title: "Week 1, Task B"
format: html
editor: visual
author: Julian Klinkmann
---

```{r}
library(tidyverse)
library(MASS)
```

#Setup 
After a short google, one finds the MASS repository, which is to simulate negative binominal distributions: [Mass rnegbin](https://stat.ethz.ch/R-manual/R-devel/library/MASS/html/rnegbin.html)

In this repo, variance is defined as follows:

> variance = mu + mu\^2/theta
This is slightly different from the description we received in our slides: \> variance=mu+mu2\*dispersion

With that we can calculate the desired variance, which is then used to predict the theta, which is needed in MASS to simulate a negative binominal distribution:

```{r}
mu <- 10 
dispersion <- 2
(var <- mu * mu^2 * dispersion)
```

Therefore, we calculate with a variance of 2000. We can calculate the necessary theta as follows:

> theta = mu\^2 / (var - mu)
So we can calculate our desired theta:

```{r}
(theta <- mu^2 / (var - mu))
```

#Create neg. bin. dist
Knowing those values, we can now evaluate our distribution. First, to assure reproducibility, we will use set.seed():

```{r}
set.seed(1000)
dist <- rnegbin(100, mu, theta)
dist
```
#Create Histogram
With all that at hand, we can visualize a histogram, in this case with the help of ggplot

```{r}
ggplot() +
  geom_histogram(mapping = aes(dist), binwidth = 2)+
  ggtitle("Histogram of negative binominal distribution: linear")
```
Now to create the logarithmic distribution, we need to take the log of our distribution:
```{r}
dist2 <- log(dist)
ggplot() +
  geom_histogram(mapping = aes(dist2), binwidth = 0.3)+
  ggtitle("Histogram of negative binominal distribution: log")
```
As we can see above, the mean `r mean(dist)` and the variance `r var(dist)` have been calculated for the linear model. 




